Towards a Classification of Sporadic $j$-invariants

### 2023-04-12 TeX/draft.tex
Update draft to better reflect rewritten code

\newcommand{\abbey}[1]{\textcolor{blue}{Abbey: #1}}

\newcommand{\sachi}[1]{\textcolor{purple}{Sachi: #1}}
% \newcommand{\travis}[1]{\textcolor{chartreuse}{Travis: #1}}

@@

\section{Riemann-Roch}

\noindent \textbf{Input:} Output from step 2\\
\textbf{Output:} Smaller list of pairs to check

@@

\section{Remaining Cases}
\abbey{Filip? Abbey?}
Filip's arguments.

>>>>

\newcommand{\abbey}[1]{\textcolor{blue}{Abbey: #1}}
\newcommand{\dld}[1]{\textcolor{Plum}{dld: #1}}
\newcommand{\sachi}[1]{\textcolor{purple}{Sachi: #1}}
% \newcommand{\travis}[1]{\textcolor{chartreuse}{Travis: #1}}

@@

\section{Filtering by Level Mapping}

\dld{This is \texttt{FilterByLevelMapping}, which used to be called
\texttt{RefuteLevel}. It acts as a filter. We feed in a list, and the output is
a (hopefully smaller) list guaranteed to contain all isolated points. If the
list is empty, then we have shown that the curve doesn't give rise to an
isolated point! If not, then perhaps other work is necessary.}

\dld{I imagine other filters being potentially applied afterwards, each
removing some set of non-isolated points.}

\begin{algorithm}[H]\label{alg:level_mapping}
  \KwIn{A list of pairs $(N, d)$ such that $E$ gives a nonCM point on $X_1(N)$
  of degree $d$.}
  \KwOut{A list of pairs $(N, d)$ containing all isolated points.}
  (sketch)\;
  create list of guaranteed nonisolated points using easy Riemann--Roch\;
  filter potentially isolated points via Theorem~\ref{BELOVthm}\;
  \Return{remaining $(N, d)$ pairs.}
\end{algorithm}

\dld{I collect the ingredients for use. The easy Riemann--Roch argument we use
is from the following lemma. In principle, we could use any source of
guaranteed nonisolated points.}

@@

\dld{For the filter, we apply (the contrapositive of) Theorem~\ref{BELOVthm}.
We also use the degree of the natural map as in Proposition~2.2 of BELOV.}

\section{Remaining Filters}
\abbey{Filip? Abbey?}
Filip's arguments.
